---
title: "advanced_visualization_with_r_part_1_exercises"
output:
  html_document:
    df_print: paged
---

#### Exercise 1 ####
# =================================================-

#### Question 1 ####

# Read the fast_food_data.csv into a dataset named "fast_food_data". 
# Set both the `header` and `stringsAsFactors` arguments equal to TRUE. 
# Subset the data set to be named "fast_food_subset" and include columns 3, 5, 6, 10, 11. 
# Then rename those columns "type", "calories","totfat","carbs", & "sugars".

# Answer: 
```{r}
fast_food_data = read.csv("data/fast_food_data.csv",header = TRUE, stringsAsFactors = TRUE)
fast_food_subset = fast_food_data[,c(3,5,6,10,11)]
head(fast_food_subset)
colnames(fast_food_subset) <- c("type", "calories","totfat","carbs","sugars")
```


#### Question 2 ####

# Create a dataset `fast_food_num`, which consists of only the numeric variables from fast_food_subset. Hint: Drop the 'type' column.
# Then retrieve the number of columns from `fast_food_num` and store it in the variable `num_col`.
# Sample `num_col` number of colors from `colors` and store it in `color_sam`. 
# Make sure to set the seed to 2 before sampling.
# What four colors did sample choose?

# Answer: May vary. Our answer is "lightgray", "lavenderblush4", "grey12", and "grey88"
```{r}
fast_food_num = fast_food_subset[,-c(1)]
num_col = ncol(fast_food_num)
set.seed(2)
color_sam = sample(colors(),size = num_col)
color_sam
```

#### Question 3 ####

# Make a boxplot of the variables in `fast_food_num` using the colors stored in `color_sam`. 
# Which variable has the widest range?

# Answer: Calories
```{r}
boxplot(fast_food_num, col = color_sam)
```

#### Question 4 ####

# Create a 2x2 grid of histograms of all 4 variables in `fast_food_num`, using colors in  `color_sam`.
# appropriately labeled with xlabel and title for each.

# Answer: 
```{r}
par(mfrow = c(2, 2))
hist(fast_food_num$calories,  
     col = color_sam[1], 
     xlab = "Calories in Fast Food",   
     main = "Distribution of Calories in Fast Food Items")
hist(fast_food_num$totfat,  
     col = color_sam[2],
     xlab = "Total Fat in Fast Food",   
     main = "Distribution of Total Fat Content in Fast Food Items")
hist(fast_food_num$carbs,  
     col = color_sam[3],
     xlab = "Carbs in Fast Food",   
     main = "Distribution of Carbs in Fast Food Items")
hist(fast_food_num$sugars,  
     col = color_sam[4],
     xlab = "Sugars in Fast Food",   
     main = "Distribution of Sugars in Fast Food Items")
```

#### Question 5 ####

# Reset the grid by running par(mfrow = c(1, 1)).
# Begin with plotting total fat against carbohydrate. Have total fat be on the x-axis and carbohydrate on the y-axis.
# Use the column index to specify the variables. Create appropriate labels for x and y axes and title.
# Fill in with triangle symbol(set pch to 17) and color "salmon2".

# Answer:
```{r}
par(mfrow = c(1, 1))
plot(x = fast_food_num$totfat, 
     y = fast_food_num$carbs,
     xlab = "Total Fat", 
     ylab = "Total Carb",
     main = "Total fat against carbohydrate",
     pch = 17,
     col = "salmon2")
```
